### 2024-05-06 README.Rmd

# archyjobads

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/archyjobads/master?urlpath=rstudio)

@@

> Poole, Anne Marie, Ailin Zhang, Setareh Shafizadeh, Jess Beck, Ben Marwick, 2024. Careers in Ruins: Academic Archaeology Job Trends From 2013 – 2023. Poster presented at the SAA annual meeting in New Orleans, 17-21 April 2024

>>>>

# Careers in Ruins: Academic Archaeology Job Trends From 2013 – 2023

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/archyjobads/master?urlpath=rstudio) [![DOI:10.17605/OSF.IO/J58K](https://img.shields.io/badge/DOI-10.17605/OSF.IO/J58KH-brightgreen.svg)](http://doi.org/10.17605/OSF.IO/J58KH)

@@

> Poole, Anne Marie, Ailin Zhang, Setareh Shafizadeh, Jess Beck, Ben Marwick, 2024. Careers in Ruins: Academic Archaeology Job Trends From 2013 – 2023. Poster presented at the SAA annual meeting in New Orleans, 17-21 April 2024. doi: 10.17605/OSF.IO/J58KH

![](README-fig-001.png)
